---
title: "Methods and Results"
author: Kristoffer Wild
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

``````{r setup, include=FALSE, eval = T, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(digits = 2)
rm(list=ls())
sessionInfo()
# Packages
pacman::p_load("dplyr", "tidyverse", "lubridate", "ggplot2", "plotly", "pbapply","car", "readr", "lmerTest", "emmeans", "AICcmodavg", "nls.multstart", "broom", "purrr", "plotrix", "AICcmodavg", "MuMIn", "stargazer", "jtools", "huxtable", "officer", "grid", "png", "ggimage", "nls.multstart", "ggrepel", "mgcv", "gratia", "gammit", "lubridate", "lmerTest","performance", "kableExtra","flextable", 'tidymv')
```
\newpage
```{r Theoretical fig, echo = FALSE, include = FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure1_Theoretical.pdf")
```
Figure 1. The comprehensive workflow of the experimental design aimed at identifying trade-offs in thermoregulation and their implications for survival. Laboratory thermal gradient experiments (A) were used to (1) measure the preferred body temperature (Tset) and (2) assess the correlation between surface temperatures (Tsurf) recorded with accelerometers and internal body temperatures, enabling the prediction of body temperatures in the field (Tb,predict). Seasonal thermoregulation and field performance metrics were evaluated using accelerometers (B). Copper pipes were placed in various microhabitats to characterise the thermal environment (Te) available to lizards in the field (C). Metrics (D) derived from experiments were then used as covariates to understand their impact on survival during the spring season, a period of high predation pressure for this species (E).
\newpage
```{r Fig2 Tb db de,echo= FALSE}
#############
###### Fig 2A|B - Tb within Tset
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
db.sex.all.final <- readRDS("Final.Analysis/Final.Figure.data/db.final.RDS")
### arranging data for figures
# Tb vs Te within Tsel across seasons 
Tb.mod <- lmer(Tb  ~ Sex + Season + Season*Sex + (1|POVI), db.sex.all.final)
Tb.mod.sum <- anova(Tb.mod) # NS Sex; Significant interaction and season
Tb.anova.pairwise <- emmeans(Tb.mod, pairwise ~ Sex |Season) # Summer differences
Tb.Sex.Season.df <- as.data.frame(Tb.anova.pairwise$emmeans) %>% 
  select(c(Season, emmean, SE, Sex, asymp.UCL , asymp.LCL))
Tb.Sex.Season.df <- Tb.Sex.Season.df %>% 
  rename(upper.CL = asymp.UCL, lower.CL = asymp.LCL)
### Te by season and sex
Te <- readRDS(file = "Final.Analysis/Final.Figure.data/Te.sex.final.RDS") 
Te.dat <- Te %>% group_by(Season, Model_.) %>% summarise(Te = mean(Te))
Te.mod <- lmer(Te  ~ Season  + (1|Model_.), Te.dat)
Te.mod.sum <- anova(Te.mod) # All different
Te.anova.pairwise <- emmeans(Te.mod, pairwise ~ Season) 
Te.Sex.Season.df <- as.data.frame(Te.anova.pairwise$emmeans) %>% 
  mutate(Sex = "Te") %>% 
  select(c(Season, emmean, SE, Sex, lower.CL, upper.CL))
# final df for figure
Tb.vs.Te.fig.dat <- rbind(Te.Sex.Season.df, Tb.Sex.Season.df)
Tb.vs.Te.fig.dat <- mutate(Tb.vs.Te.fig.dat, Season = factor(Season,
                                                             levels = c("Spring",
                                                                        "Summer",
                                                                        "Autumn",
                                                                        "Winter"))) %>%
  group_by(Season)
# Sex      IQR  Mean.Tb    range upper.IQR lower.IQR
# ZZm 6.700000 28.68080 3.350000  32.03080  25.33080
# bring in activity data
Male.Tb.Te <- Tb.vs.Te.fig.dat %>% filter(Sex != "ZWf")
Male.Tb.Te$Sex <- gsub("ZZm", "Male", Male.Tb.Te$Sex)
Male.Tb.Te <- mutate(Male.Tb.Te, Sex = factor(Sex, levels = c("Te","Male"))) %>%
  group_by(Sex)
######
### Male plot Fig 2A # ~T[b]
Male.Tb.vs.Te.fig <- ggplot(Male.Tb.Te, aes(x=Season, y=emmean, colour=Sex, group=Sex, shape = Sex)) +
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), colour="black", width=.25) +
  geom_point(aes(shape=Sex, color=Sex), size=3)+
  geom_line(aes(linetype=Sex)) +
  scale_shape_manual(values=c(8, 19))+
  scale_color_manual(values=c("black","steelblue")) +
  geom_hline(yintercept=32.03080, linetype="dashed", color = "grey34")+
  geom_hline(yintercept=25.33080, linetype="dashed", color = "grey34")+ 
  scale_y_continuous(breaks=c(18, 20, 22, 24, 26, 28, 30, 32, 34, 36))+
  coord_cartesian(ylim = c(18, 36))+
  annotate("text", x = 1.25, y = 35.8, label = expression(bold("Male T"["b"])), fontface = "bold", size = 7) +
  annotate("text", x = 4, y = 32.6, label = "Tset upper")+
  annotate("text", x = 4, y = 24.8, label = "Tset lower")+
  xlab(NULL) +
  ylab(expression(~T["b perdict"]~ "(°C)"))+
  theme_classic() + 
  theme(legend.position = c(.85, .9),
                          legend.title = element_blank(), 
                          legend.background = element_rect(fill = "transparent", color = NA), # Make legend background transparent
                          legend.box.background = element_rect(fill = "transparent", color = NA), # Ensure the legend box is also transparent
                          axis.title.x = element_blank(),
                          axis.text.x = element_blank(),
                          text = element_text(size = 18))
# ZWf 6.833333 30.38976 3.416667  33.80642  26.97309
Female.Tb.Te <- Tb.vs.Te.fig.dat %>% filter(Sex != "ZZm")
Female.Tb.Te$Sex <- gsub("ZWf", "Female", Female.Tb.Te$Sex)
Female.Tb.Te <- mutate(Female.Tb.Te, Sex = factor(Sex, levels = c("Te","Female"))) %>%
  group_by(Sex)

######
### Female Plot Fig 2B
Female.Tb.vs.Te.fig <- ggplot(Female.Tb.Te, aes(x=Season, y=emmean, colour=Sex, group=Sex, shape = Sex)) + 
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), colour="black", width=.25) +
  geom_point(aes(shape=Sex, color=Sex), size=3)+
  geom_line(aes(linetype=Sex)) +
  scale_shape_manual(values=c(8, 19))+
  scale_color_manual(values=c("black", "darkred")) +
  geom_hline(yintercept=33.80642, linetype="dashed", color = "grey34")+
  geom_hline(yintercept=26.97309, linetype="dashed", color = "grey34")+   
  scale_y_continuous(breaks=c(18, 20, 22, 24, 26, 28, 30, 32, 34, 36))+
  coord_cartesian(ylim = c(18, 36))+
  annotate("text", x = 1.25, y = 35.8, label = expression(bold("Female T"["b"])), fontface = "bold", size = 7) +
  annotate("text", x = .9, y = 34.3, label = "Tset upper")+
  annotate("text", x = .9, y = 26.4, label = "Tset lower")+
  ylab(expression(~T["b perdict"]~ "(°C)"))+
  xlab(NULL)+
  theme_classic() + 
  theme(legend.position = c(.85, .9),
        legend.title = element_blank(), 
        legend.background = element_rect(fill = "transparent", color = NA), # Make legend background transparent
        legend.box.background = element_rect(fill = "transparent", color = NA), # Ensure the legend box is also transparent
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        text = element_text(size = 18))
######
### Fig2A|B Final:TB by sex
Fig.2.Tb.Te.figure <- ggpubr::ggarrange(Male.Tb.vs.Te.fig, Female.Tb.vs.Te.fig,
                                        labels = c("A", "B"), 
                                        font.label = list(size = 20), 
                                        hjust = - 0.95,
                                        vjust = 2.0 ,
                                        ncol = 2, nrow = 1)

#############
##### Fig 2C - Accuracy of thermoregulation male and females
E_final_season <- readRDS(file = "Final.Analysis/Final.Figure.data/E_season_sex_individual.RDS")
### arrange data for figure
db.mod <- lmer(mean_individual_mean_db  ~ Sex + Season + Season*Sex + (1|POVI), E_final_season)
db.mod.Sum <- anova(db.mod) # season and season*sex sig 
db.mod.anova.pairwise <- emmeans(db.mod, pairwise ~ Sex |Season) 
season.db <- as.data.frame(db.mod.anova.pairwise$emmeans)# significant difference spring
Season <- c("Spring","Summer","Autumn", "Winter")
season.db$Season <- factor(season.db$Season, levels = Season)
season.db$Sex <- gsub("ZZm", "Male", season.db$Sex)
season.db$Sex <- gsub("ZWf", "Female", season.db$Sex)
######
### 2C db plot by sex
Fig.2C.Accuracy.Thermoregulation.db <- ggplot(season.db, aes(x=Season, y=emmean, colour=Sex, group=Sex, shape = Sex)) +
  geom_errorbar(aes(ymin=emmean-SE, ymax= emmean+SE), colour="black", width=.25) +
  geom_line(aes(linetype=Sex)) +
  geom_point(aes(shape=Sex, color=Sex), size=3) +
  scale_shape_manual(values=c(19, 19), labels = c("db Female", "db Male")) +
  scale_color_manual(values=c("darkred", "steelblue"), 
                     labels = c("db Female", "db Male")) +
  scale_linetype_manual(values=c("solid", "dashed"), labels = c("db Female", "db Male")) +
  scale_y_continuous(breaks=c(0, 1, 2, 3, 4.0, 5, 6, 7, 8, 9)) +
  coord_cartesian(ylim = c(0, 9)) +
  ylab(expression("Thermoregulation accuracy (" ~d["b"]~")")) +
  #annotate("text", x = 1.5, y = 0, label = "Accurate", fontface = "bold", size = 7) +
  #annotate("text", x = 1.5, y = 8.95, label = "Inaccurate", fontface = "bold", size = 7) +
  annotate("text", x = 1, y = 3.2, label = "*", fontface = "bold", size = 9) + # spring differences
  xlab(NULL) +
  theme_classic() +
  theme(legend.position = c(.85, .1), 
        legend.title = element_blank(), 
        text = element_text(size = 18))

######
### Fig 2D de values for individual models by season
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
Te <- readRDS(file = "Final.Analysis/Final.Figure.data/Te.sex.final.RDS") %>% 
  group_by(Model_., Season, Type, Te.Analysis) %>% 
  summarise(de = mean(de))

######
### arranging data for plot
definal.mod <- lmer(de ~ Te.Analysis + Season + Te.Analysis*Season + + (1|Model_.), Te)
de.anova.sum <- round(as.data.frame(anova(definal.mod)), digits = 3) %>% mutate("Pr(>F)" = "< 0.01")# significant season sex interaction
de.mod.season.sex <- emmeans(definal.mod, pairwise ~ Te.Analysis | Season) # this just says the available environment is easier for females to thermoregulate other than in winter it's the same
de.mod.season.sex.tbl<- as.data.frame(de.mod.season.sex$emmeans)
Season <- c("Spring","Summer","Autumn", "Winter")
de.mod.season.sex.tbl$Season <- factor(de.mod.season.sex.tbl$Season, levels = Season)
de.mod.season.sex.tbl$Te.Analysis <- gsub("de_ZZm", "de Male", de.mod.season.sex.tbl$Te.Analysis)
de.mod.season.sex.tbl$Te.Analysis <- gsub("de_ZWf", "de Female", de.mod.season.sex.tbl$Te.Analysis)
######
### Fic 2D de plot
Fig.2D.Accuracy.Thermoregulation.de <- ggplot(de.mod.season.sex.tbl, aes(x=Season, y=emmean, colour=Te.Analysis, group=Te.Analysis, shape = Te.Analysis)) +
  geom_errorbar(aes(ymin=emmean-SE, ymax=emmean+SE), colour="black", width=.25) +
  geom_line(aes(linetype=Te.Analysis)) +
  geom_point(aes(shape=Te.Analysis, color=Te.Analysis), size=3)+
  scale_shape_manual(values=c(19, 19))+
  scale_color_manual(values=c("darkred", "steelblue")) +
  scale_y_continuous(breaks=c(0, 1, 2, 3, 4.0, 5, 6, 7, 8, 9, 10))+
  coord_cartesian(ylim = c(0, 10))+
  ylab(expression("Thermal quality of habitat (" ~d["e"]~")"))+
  #annotate("text", x = 1.5, y = 0, label = "Favorable",fontface = "bold", size = 7)+
  #annotate("text", x = 1.5, y = 10, label = "Unfavorable", fontface = "bold", size = 7)+
  annotate("text", x = 2, y = 4.5, label = "*", fontface = "bold", size = 9)+ # summer differences
  xlab(NULL)+
  theme_classic() +
  theme(legend.position = c(.85, .1))+ 
  theme(legend.title = element_blank(),
        text = element_text(size = 18))
######
# final arrangment for 2C & 2D
Fig.2.db.de.figure <- ggpubr::ggarrange(Fig.2C.Accuracy.Thermoregulation.db, Fig.2D.Accuracy.Thermoregulation.de,
                                        labels = c("C", "D"),
                                        font.label = list(size = 20), 
                                        hjust = - 0.95,
                                        vjust = 2.0 ,
                                        ncol = 2, nrow = 1)
######
# FINAL FIGURE MERGE
Figure_2_final <- ggpubr::ggarrange(Fig.2.Tb.Te.figure, 
                                    Fig.2.db.de.figure, 
                                    hjust = - 0.95,
                                    vjust = 2.0 ,
                                    ncol = 1, nrow = 2)

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure2_Thermal_Pars.pdf")
```
Figure 2. Mean environmental temperature (Te), thermal preference (Tset), and predicted body temperature (Tb,predict) for male (A) and female (B) Pogona vitticeps during each season. Accuracy of thermoregulation (db) between sex, where low values indicate body temperature was closer to thermal preference (C). The thermal quality of habitat (de), measured with copper models, accounted for sex differences in thermal preference (D). Low de values indicate more environmental temperatures fell within Tset (i.e. favourable thermal environment). Error bars for all panels are ±1 standard error of the mean. In all panels, males are denoted with open circles and dashed lines, and females are denoted with closed grey circles and solid lines. The asterisk symbol indicates a significant difference (P<0.01) when comparing mean differences between sexes for that season using a Tukey-Kramer post-hoc test
\newpage
```{r Fig3,echo= FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
######
### arranging data
E_final_season <- readRDS(file = "Final.Analysis/Final.Figure.data/E_season_sex_individual.RDS")
E_final_season$Season <- factor(E_final_season$Season, c("Spring", "Summer", "Autumn", "Winter"))
E.mod <- lmer(indvidual_season_E  ~ Sex + Season + Season*Sex + (1|POVI), E_final_season)
E.mod.Sum <- anova(E.mod) # significant all around
E.anova.pairwise <- emmeans(E.mod, pairwise ~ Sex |Season)
Season <- as.data.frame(E.anova.pairwise$emmeans)
Season$Sex <- gsub("ZWf", "Female", Season$Sex)
Season$Sex <- gsub("ZZm", "Male", Season$Sex)
######
### Figure 3 plot
Fig.3.E.index.fig <- ggplot(Season, aes(x=Season, y=emmean, fill=Sex)) + 
  scale_y_continuous(breaks=c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0))+
  coord_cartesian(ylim = c(-0.3, 1.0))+
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=emmean -SE, ymax=emmean +SE), width=.2,
                position=position_dodge(.9))+
  labs(x="Season", y = "E index")+
  #annotate("text", x = 1.5, y = .95, label = "Thermoregulator",fontface = "bold")+
  #annotate("text", x = 1.5, y = -.05, label = "Thermoconformer", fontface = "bold")+
  annotate("text", x = .9, y = .86, label = "*", fontface = "bold", size = 8)+ # spring differences
  geom_segment(aes(x = .6, y = .85, xend = 1.2, yend = .85))+
  scale_fill_manual(values=c("darkred", "steelblue"))+
  theme_classic() +
  theme(legend.position=c(.90, .80),
        text = element_text(size = 18))

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure3_Eindex.pdf")
```
Figure 3. Effectiveness of thermoregulation (E index) by sex and season in Pogona vitticeps. Values represent the means accounting for all individuals for each season. Error bars indicate ±1 standard error of the mean. The asterisk symbol denotes a significant difference (P<0.01) between sexes when comparing mean differences for that season using a Tukey-Kramer post-hoc test.  
\newpage
```{r Fig4 HR activity tb te,echo= FALSE}
#############
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
##### Fig 4 -Activity, Tb, Te, Tset by hour
Tb.predict.dat <- readRDS(file = "Final.Analysis/Final.Figure.data/Final.Activity.mins.data.RDS") %>% filter(Sex != "ZZf")
Tb.predict.dat$Hour <- as.factor(Tb.predict.dat$HR)
# summary
Male.Tb <- Tb.predict.dat%>% filter(Sex != "ZWf") %>% 
  group_by(Date, Hour) %>% 
  ungroup() %>% 
  group_by(Hour, Season, Sex) %>% 
  summarise(Tb = mean(Tb),
            HR = unique(HR))
Male.Tb$Season <- factor(Male.Tb$Season, c("Spring", "Summer", "Autumn", "Winter"))
# activity data
mydata.final.mm<- readRDS(file = "Final.Analysis/Final.Figure.data/activity.fig.data.rds")
Male.Activity <- mydata.final.mm %>% filter(Sex != "ZWf")
Male.Activity$Season <- factor(Male.Activity$Season, c("Spring", "Summer", "Autumn", "Winter"))

# Te data
Te <- readRDS(file = "Final.Analysis/Final.Figure.data/Te.sex.final.RDS") 
Te$Type <- gsub("open_tree", "Open_tree", Te$Type)
Te.data.fig <- Te %>% 
  group_by(hr, Season, Type) %>% 
  summarise(Te = mean(Te),
            HR = unique(HR))
Te.data.fig$Season <- factor(Te.data.fig$Season, c("Spring", "Summer", "Autumn", "Winter"))

# male plot
# Define your custom color palette
custom_colors <- c(
  "Burrow" = "grey50",     # Sandy Brown
  "Full_Shade" = "springgreen2", 
  "Open" = "#DAA505",       # Goldenrod
  "Open_tree" = "#8B4513",  # Saddle Brown
  "Tree" = "seagreen4"        # Dark Olive Green
)

male.tb.te.act.fig <- ggplot() +  
  geom_point(data = Te.data.fig, aes(HR, Te, fill = Type, color = Type)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Activity (min/hr)")) +
  geom_line(data = Male.Activity, aes(HR, Movement.HR), size = 0.3) +
  geom_hline(yintercept = 32.03080, linetype = "dashed", color = "grey34") +
  geom_hline(yintercept = 25.33080, linetype = "dashed", color = "grey34") + 
  labs(x = NULL, y = "Temperature (°C)", fill = "Habitat", color = "Habitat") +
  facet_grid(~ Season, labeller = as_labeller(c("Spring" = "Spring",
                                                "Summer" = "Summer",
                                                "Autumn" = "Autumn",
                                                "Winter" = "Winter"))) +
  coord_cartesian(xlim = c(5, 21)) +
  scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
  geom_line(data = Male.Tb, aes(HR, Tb), size = 0.3) +
  geom_point(data = Male.Tb, aes(HR, Tb), 
             fill = "white", color = "steelblue",
             size = 2.2, shape = 21) +
  geom_point(data = Male.Activity, aes(HR, Movement.HR), 
             fill = "steelblue", color = "black", 
             size = 2, shape = 17) +
  theme_bw() +
  theme(legend.position = c(0.85, 0.85), # Adjust the legend position as needed
    legend.background = element_rect(fill = alpha('white', 0)), # Fully transparent legend background
    legend.box = "vertical", # Arrange legend in vertical boxes
    legend.box.spacing = unit(0.5, "cm"), # Space between legend boxes
    text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"), # Customize legend title
    legend.text = element_text(size = 12), # Customize legend text size
    strip.background = element_blank(), # Remove gray boxes from facets
    strip.text.x = element_text(size = 16, face = "bold"), # Customize facet labels
    plot.title = element_blank(), # Remove the plot title
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    panel.background = element_blank(), # Remove panel background
    panel.border = element_rect(color = "black", fill = NA))+ # Keep panel border
    guides(fill = guide_legend(ncol = 2), 
           color = guide_legend(ncol = 2))


# female
Female.Tb <- Tb.predict.dat%>% filter(Sex != "ZZm") %>% 
  group_by(Date, Hour) %>% 
  ungroup() %>% 
  group_by(Hour, Season, Sex) %>% 
  summarise(Tb = mean(Tb),
            HR = unique(HR))
Female.Tb$Season <- factor(Female.Tb$Season, c("Spring", "Summer", "Autumn", "Winter"))
# activity data
Female.Activity <- mydata.final.mm %>% filter(Sex != "ZZm")
Female.Activity$Season <- factor(Female.Activity$Season, c("Spring", "Summer", "Autumn", "Winter"))
female.tb.te.act.fig <- ggplot() +  
  geom_point(data = Te.data.fig, aes(HR, Te, fill = Type, color = Type)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Activity (min/hr)")) +
  geom_line(data = Female.Activity, aes(HR, Movement.HR), size = 0.3) +
  geom_hline(yintercept = 32.03080, linetype = "dashed", color = "grey34") +
  geom_hline(yintercept = 25.33080, linetype = "dashed", color = "grey34") + 
  labs(x = 'Time of day (h)', y = "Temperature (°C)", fill = "Habitat", color = "Habitat") +
  facet_grid(~ Season, labeller = as_labeller(c("Spring" = "Spring",
                                                "Summer" = "Summer",
                                                "Autumn" = "Autumn",
                                                "Winter" = "Winter"))) +
  coord_cartesian(xlim = c(5, 21)) +
  scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
  geom_line(data = Female.Tb, aes(HR, Tb), size = 0.3) +
  geom_point(data = Female.Tb, aes(HR, Tb), 
             fill = "white", color = "darkred",
             size = 2.2, shape = 21) +
  geom_point(data = Female.Activity, aes(HR, Movement.HR), 
             fill = "black", color = "black", 
             size = 2, shape = 17) +
  theme_bw() +
  theme(legend.position = c(0.85, 0.85), # Adjust the legend position as needed
    legend.background = element_rect(fill = alpha('white', 0)), # Fully transparent legend background
    legend.box = "vertical", # Arrange legend in vertical boxes
    legend.box.spacing = unit(0.5, "cm"), # Space between legend boxes
    text = element_text(size = 16),
    legend.title = element_text(size = 14, face = "bold"), # Customize legend title
    legend.text = element_text(size = 12), # Customize legend text size
    strip.background = element_blank(), # Remove gray boxes from facets
    strip.text.x = element_text(size = 16, face = "bold"), # Customize facet labels
    plot.title = element_blank(), # Remove the plot title
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    panel.background = element_blank(), # Remove panel background
    panel.border = element_rect(color = "black", fill = NA))+ # Keep panel border
    guides(fill = guide_legend(ncol = 2), 
           color = guide_legend(ncol = 2))


#############
# Fig4 Final: Tb, Te, Activity
Fig.4.Tb.Te.Activity.fig<- ggpubr::ggarrange(male.tb.te.act.fig, female.tb.te.act.fig,
                                  font.label = (size = 32), 
                                  hjust = - 0.7,
                                  vjust = 2.0 ,
                                  labels = c( "A-Male", "B-Female"),
                                  ncol = 1, nrow = 2)

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure4_Activity_Tbs.pdf")
```
Figure 4. Predicted body temperatures (lines with circles) and activity levels (lines with triangles) for male (A) and female (B) Pogona vitticeps by time of day. The dashed line represents their preferred body temperature ranges. Coloured circles indicate mean environmental temperatures for different habitat types, measured using copper models.  
\newpage
```{r Fig5 TPC ,echo= FALSE}
#############
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
##### TPC data
# Step 1: Read and Filter Data
your_data <- readRDS(file = "Final.Analysis/Final.Figure.data/data.temp.gam.analysis.rds") %>% 
  filter(Sex != 'ZZf')

# Step 2: grab fit from the GAM Model
gam_model <- readRDS(file = "Models/Season.Sex.Interaction.Povi.rds")
gam_model_data <- plot_smooths(Season.Sex.Interaction.Povi, temp, Sex, facet_terms = Season)
gam_model_data <- as.data.frame(gam_model_data$data)

# SPRING
Spring <- gam_model_data %>% filter(Season == "Spring")
Spring.plot <- ggplot() +  
  geom_point(data = your_data %>% 
               filter(Season == "Spring"), 
             aes(x = temp, y = percent95.ms2, shape = Sex, color = Sex), size = 2) +
  scale_shape_manual(values = c(17, 21)) +
  scale_color_manual(values = c( 'darkred', "steelblue"), labels = c("Female", "Male")) +
  scale_fill_manual(values = c('darkred', "steelblue")) +  # Ensure fill colors for the ribbon
  ylab(bquote("95th"~"percentile"~"of"~"acceleration ms"^-2)) +
  xlab(expression(T[b~Predict])) +
  coord_cartesian(xlim = c(10, 50), ylim = c(0.06, 1.8)) +
  scale_x_continuous(breaks = seq(10, 50, 5)) +
  scale_y_continuous(breaks = seq(0, 1.8, .2)) +
  geom_ribbon(data = Spring, aes(x = temp, ymin = CI_lower, 
                                 ymax = CI_upper, fill = Sex), alpha = 0.2) +
  geom_line(data = Spring, aes(x = temp, y = percent95.ms2, color = Sex), size = 1) +  
  theme_bw() +
  ggtitle("Spring") +
  theme(legend.position = "none",
        text = element_text(size = 16),
        plot.title = element_text(size = 18, 
                                  face = "bold", hjust = 0.5),
        panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank())



###### Summer
Summer <- gam_model_data %>% filter(Season == "Summer")
Summer.plot <- ggplot() +  
  geom_point(data = your_data %>% filter(Season == "Summer"), aes(x = temp, y = percent95.ms2, shape = Sex, color = Sex), size = 2) +
  scale_shape_manual(values = c(17, 21)) +
  scale_color_manual(values = c( 'darkred', "steelblue"), labels = c("Female", "Male")) +
  scale_fill_manual(values = c('darkred', "steelblue")) +
  ylab(NULL) +  # Remove Y-axis label
  xlab(expression(T[b~Predict])) +
  coord_cartesian(xlim = c(10, 50), ylim = c(0.06, 1.8)) +
  scale_x_continuous(breaks = seq(10, 50, 5)) +
  scale_y_continuous(breaks = seq(0, 1.8, .2)) +
  geom_ribbon(data = Summer, aes(x = temp, ymin = CI_lower, 
                                 ymax = CI_upper, fill = Sex), alpha = 0.2) +
  geom_line(data = Summer, aes(x = temp, y = percent95.ms2, color = Sex), size = 1)+
  theme_bw() +
  ggtitle("Summer") +
  theme(legend.position = "none",
        text = element_text(size = 16),
        plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
        panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank())


###### Autumn
Autumn <- gam_model_data %>% filter(Season == "Autumn")
Autumn.plot <- ggplot() +  
  geom_point(data = your_data %>% filter(Season == "Autumn"), 
             aes(x = temp, y = percent95.ms2, shape = Sex, color = Sex), size = 2) +
  scale_shape_manual(values = c(17, 21)) +
  scale_color_manual(values = c( "darkred", "steelblue"), labels = c("Female", "Male")) +
  scale_fill_manual(values = c('darkred', "steelblue")) +
  xlab(expression(T[b~Predict])) +
  ylab(NULL) +  # Remove Y-axis label
  coord_cartesian(xlim = c(10, 50), ylim = c(0.06, 1.8)) +
  scale_x_continuous(breaks = seq(10, 50, 5)) +
  scale_y_continuous(breaks = seq(0, 1.8, .2)) +
  geom_ribbon(data = Autumn, aes(x = temp, ymin = CI_lower, 
                                 ymax = CI_upper, fill = Sex), alpha = 0.2) +
  geom_line(data = Autumn, aes(x = temp, y = percent95.ms2, color = Sex), size = 1)+
  theme_bw() +
  ggtitle("Autumn") +
  theme(legend.position = "none",
        text = element_text(size = 16),
        plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
        panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank())   # Remove minor grid lines



###### Winter
Winter <- gam_model_data %>%filter(Season == "Winter") 

Winter.plot <- ggplot() +  
  geom_point(data = your_data %>% filter(Season == "Winter"), 
             aes(x = temp, y = percent95.ms2, shape = Sex, color = Sex), size = 2) +
  scale_shape_manual(values = c(17, 21), labels = c("Female", "Male")) +
  scale_color_manual(values = c( 'darkred', "steelblue"), labels = c("Female", "Male")) +
  scale_fill_manual(values = c('darkred', "steelblue")) +
  ylab(NULL) +  # Remove Y-axis label
  xlab(expression(T[b~Predict])) +
  coord_cartesian(xlim = c(10, 50), ylim = c(0.06, 1.8)) +
  scale_x_continuous(breaks = seq(10, 50, 5)) +
  scale_y_continuous(breaks = seq(0, 1.8, .2)) +
  geom_ribbon(data = Winter, aes(x = temp, ymin = CI_lower, 
                                 ymax = CI_upper, fill = Sex), alpha = 0.2) +
  geom_line(data = Winter, aes(x = temp, y = percent95.ms2, color = Sex), size = 1)+
  theme_bw() +
  ggtitle("Winter") +
  theme(
    text = element_text(size = 16),
    legend.position = c(0.94, 0.98),  # Position legend inside the plot area
    legend.justification = c(1, 1),  # Adjust legend justification
    legend.background = element_rect(fill = "transparent", color = NA),  # Make legend background transparent
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank())+   # Remove minor grid lines
  guides(shape = guide_legend(title = "Sex"), 
         color = guide_legend(title = "Sex"), 
         fill = "none")  # Remove the fill legend



Figure_5_TPC<- cowplot::plot_grid(Spring.plot, Summer.plot, Autumn.plot, Winter.plot, ncol=4)

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure5_TPC.pdf")
```
Figure 5. Thermal performance curves of free-ranging Pogona vitticeps across different seasons and sex. The data were obtained from the top-performing Generalized Additive Mixed Models (GAMM) presented in Table S5. Each data point represents the average performance (95th percentile of acceleration) at a given temperature for all individuals in each season and sex. Females are represented by triangles and grey fitted lines, while males are represented by open circles and black fitted lines. Light grey bands around lines indicate the 95% confidence interval of the model fit
```{r Fig6 HR activity tb te,echo= FALSE}
############################################################
#####  #####  #####  #####  #####  #####  #####  #####  #####  
#####  #####  #####  SURIVAL #####  #####  #####  #####  #####  
# MARK OUTPUT
setwd('~/Dropbox/RWorkingDirectory/TPC_Survival/R')
dat <- read.csv(file = "Final.Analysis/Final.Figure.data/MARK_Outputs/Sex_Topt_survival.csv") %>% 
  rename(Survival = Survial)
Figure_6_survival <- ggplot(dat, aes(x = Pmax * 100, # back transform because MARK makes you put parameters in 0-1
                                 y = Survival, color = Sex, linetype = Sex)) + 
  geom_line(size = 1) + 
  geom_ribbon(aes(ymin = Survival - SE, ymax = Survival + SE, fill = Sex), alpha = 0.2) +
  scale_fill_manual(values = c("darkred", "steelblue")) +  # Different shades of grey for ribbon fill
  scale_linetype_manual(values = c("solid", "longdash")) +  
  scale_color_manual(values = c("grey60", "black")) +  
  labs(x = expression(95^th ~ percentile ~ of ~ acceleration ~ (ms^{-2})), y = "Survival") + 
  theme_bw() +
  theme(
    text = element_text(size = 18),  # Set text size
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "white", colour = NA), 
    legend.position = c(0.90, 0.90),
    legend.background = element_rect(fill = "transparent")
  )

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/Figure6_Survival.pdf")
```
Figure 6. Survivorship as a function of the maximum performance (Pmax) for free-ranging Pogona vitticeps. Data are extracted from the top candidate model in program Mark (Table S8). 



# Supplement Tables & Figures
Table S1. Microhabitat categories of sun exposure. At each micro-habitat category, copper pipes were placed at each cardinal direction. Sun% was calculated using a spherical densiometer. 
\newpage
Table S2. ANOVA table for predicted body temperature (Tb Predict), accuracy of thermoregulation (db), thermal quality of habitat (de), and effectiveness of thermoregulation (E) for Pogona vitticeps. Each estimate is compared across the season, sex, and interaction. Individual lizard (or copper model ID) was treated as a repeated (random) variable. Bold values indicate significant differences.
```{r TB,echo= FALSE}
# bring in, combined and rename tables
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
#######
# Tb body temperature 
#######
db.sex.all.final <- readRDS(file = "Final.Analysis/Final.Figure.data/db.final.RDS")
Tb.sample.size <- db.sex.all.final %>% ungroup() %>% group_by(Season) %>% summarise(n =n())
Tb.mod <- lmer(Tb  ~ Sex + Season + Season*Sex + (1|POVI), db.sex.all.final)
Tb.mod.sum <- round(as.data.frame(anova(Tb.mod)), digits = 2) %>% mutate("Model Name" = "Tb Predict") 
Tb.mod.sum[2,6] <- "<0.01"
Tb.mod.sum[3,6] <- "<0.01"
#######
# db values 
#######
# note these data are summarised by inividual, date, by the hour. Season, sex are unique
db.final.mod <- lmer(individual_db ~ Sex + Season + Season*Sex + (1|POVI), db.sex.all.final)
db.anova.sum <- round(as.data.frame(anova(db.final.mod)), digits = 2)%>% mutate("Model Name" = "db") 
db.anova.sum[2,6] <- "<0.01"
db.anova.sum[3,6] <- "<0.01"
####################  
# de values 
####################  
#analysis for de by sex and season
Te <- readRDS(file = "Final.Analysis/Final.Figure.data/Te.sex.final.RDS") %>% 
  group_by(Model_., Season, Type, Te.Analysis) %>% 
  summarise(de = mean(de))
definal.mod <- lmer(de ~ Te.Analysis + Season + Te.Analysis*Season + (1|Model_.), Te)
de.anova.sum <- round(as.data.frame(anova(definal.mod)), digits = 2) %>% mutate("Model Name" = "de")
de.anova.sum[1,6] <- "<0.01"
de.anova.sum[2,6] <- "<0.01"
de.anova.sum[3,6] <- "0.01"
####################  
# Eindex 
####################  
E_final_season <- readRDS(file = "Final.Analysis/Final.Figure.data/E_season_sex_individual.RDS")
E.mod <- lmer(indvidual_season_E  ~ Sex + Season + Season*Sex + (1|POVI), E_final_season)
E.mod.Sum <- round(as.data.frame(anova(E.mod)), digits = 2) %>% mutate("Model Name" = "E")
E.mod.Sum[2,6] <- "<0.01"
E.mod.Sum[3,6] <- "<0.01"


###
# Final DF merge
###
Table2 <- rbind(Tb.mod.sum, db.anova.sum, de.anova.sum, E.mod.Sum)
Table2 <- Table2 %>% mutate_if(is.numeric, ~round(., 3)) %>% as.data.frame() %>% mutate(Effects = "")
Table2[1,8] <- "Sex"
Table2[2,8] <- "Season"
Table2[3,8] <- "Season x Sex"
Table2[4,8] <- "Sex"
Table2[5,8] <- "Season"
Table2[6,8] <- "Season x Sex"
Table2[7,8] <- "Sex"
Table2[8,8] <- "Season"
Table2[9,8] <- "Season x Sex"
Table2[10,8] <- "Sex"
Table2[11,8] <- "Season"
Table2[12,8] <- "Season x Sex"
Table2  <-  Table2[,c(7,8,1,2,3,4,5,6)]
# Table1 Final table
Tbl.S2 <-flextable(Table2) %>% 
  hline(i=c(3, 6, 9, 12), j = 1:8, part="body") %>% 
  merge_v(j = "Model Name") %>%  
  autofit(part = "all") %>% 
  bold(bold = TRUE, i = c(2, 3, 5, 6, 7, 8, 9, 11, 12)) %>% 
  bold(bold = FALSE, j = 1) %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S2)
```

\newpage
Table S3. Tukey-Kramer multiple comparisons from Tb predict model (Table 2). Contrasts were extracted from overall seasonal effect.  
```{r S3, echo = FALSE, include = FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
db.sex.all.final <- readRDS(file = "Final.Analysis/Final.Figure.data/db.final.RDS")
Tb.sample.size <- db.sex.all.final %>% ungroup() %>% group_by(Season) %>% summarise(n =n())
Tb.mod <- lmer(Tb  ~ Sex + Season + Season*Sex + (1|POVI), db.sex.all.final)
Tb.anova.pairwise.season <- emmeans(Tb.mod, pairwise ~ Season, lmerTest.limit = 67884) 

# Table S3
S3.Tb.Sex.Season.tbl <- as.data.frame(Tb.anova.pairwise.season$contrasts) %>%
  mutate_if(is.numeric, ~round(., 2))
S3.Tb.Sex.Season.tbl[1,6]= "<0.01"
S3.Tb.Sex.Season.tbl[2,6]= "<0.01"
S3.Tb.Sex.Season.tbl[3,6]= "<0.01"
S3.Tb.Sex.Season.tbl[4,6]= "<0.01"
S3.Tb.Sex.Season.tbl[5,6]= "<0.01"
S3.Tb.Sex.Season.tbl[6,6]= "<0.01"
Tbl.S3 <-flextable(S3.Tb.Sex.Season.tbl) %>% 
  autofit(part = "all") %>% 
  bold(bold = TRUE, i = c(1,2,3,4,5,6)) %>%
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman")

knitr::knit_print(Tbl.S3)
```
\newpage
Table S4. Tukey-Kramer multiple comparisons of overall seasonal activity rate (min/hr). Activity rate was log (x+1) scale for all *P. vitticeps*. 
```{r S4,echo= FALSE}
# bring in, combined and rename tables
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
# raw acceleration points before summary
raw.data <- readRDS(file = "Final.Analysis/Final.Figure.data/avg.min.final.clean.RDS")
raw.data.sample.size <- nrow(raw.data)
# Analysis - Accelerometer Note: Needed to log transform movement min +1log because of high frequencies of zeros
act.analysis.dat <- readRDS(file = "Final.Analysis/Final.Figure.data/activity.season.sex.analysis.data.RDS")
activity.analysis.mod <- lmer(log1p(Movement.HR)  ~ Sex + Season + Season*Sex + (1|POVI), act.analysis.dat)
activity.analysis.mod.final <- as.data.frame(anova(activity.analysis.mod)) # no differences in sex or interaction; season had largest effect 
Activity.pairwise <- emmeans(activity.analysis.mod, pairwise ~ Season) # sex differences in the spring and summer
Activity.Season.tbl <- as.data.frame((Activity.pairwise$contrasts))
Activity.Season.tbl <- Activity.Season.tbl %>% mutate_if(is.numeric, ~round(., 2))
Activity.Season.tbl[3,6]= "<0.01"
Activity.Season.tbl[5,6]= "<0.01"

# Table4 Final table
Tbl.S4 <-flextable(Activity.Season.tbl) %>% 
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  bold(bold = TRUE, i = c(3,5,6)) %>%
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S4)
```
\newpage
Table S5. General additive mixed-models for investigating how performance curves varied across season, sex and their interactions for *Pogona vitticeps*. a) accounted for all individuals in study, b) accounted for smooth per individual, c) accounted for sex as a fixed factor, d) accounted for sex as a fixed factor and allowed for smooth per individual, e) accounted for season as a fixed factor, f) accounted for season as a fixed factor and allowed for smooth per individual, g) accounted for season and sex as a fixed factor, h) accounted for season and sex as a fixed factor and allowed for smooth per individual, i) accounted for season, sex, and their interaction as a fixed factor, and j) accounted for season, sex, and their interaction as a fixed factor and allowed for smooth per individual. Models b:j accounted for random intercept for individual lizard.
```{r S5,echo= FALSE}
# bring in, combined and rename tables
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
Temp <- readRDS(file = "Models/Temp.rds")
Temp.Povi <- readRDS(file = "Models/Temp.Povi.rds")
Sex <- readRDS(file = "Models/Sex.rds")
Sex.Povi <- readRDS(file = "Models/Sex.Povi.rds")
Season <- readRDS(file = "Models/Season.rds")
Season.Povi <- readRDS(file = "Models/Season.Povi.rds")
Season.Sex <- readRDS(file = "Models/Season.Sex.rds")
Season.Sex.Povi <- readRDS(file = "Models/Season.Sex.Povi.rds")
Season.Sex.Interaction <- readRDS(file = "Models/Season.Sex.Interaction.rds")
Season.Sex.Interaction.Povi <- readRDS(file = "Models/Season.Sex.Interaction.Povi.rds")

# final table using all of the gam's above
gam.table <- read.csv("Final.Analysis/Final.Figure.data/GAMM.anova.table.csv",dec = "2")
TableS5 <- gam.table

# Table S5 Final table
Tbl.S5 <-flextable(TableS5) %>% 
  autofit(part = "all") %>%  
  align(align ="center", j = c(1,3,4,5,6,7)) %>% 
  bold(bold = TRUE, i = c(1)) %>%
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S5)
```
\newpage
Table S6. Tukey-Kramer multiple comparisons from Pmax model that accounted for season, sex and the interaction. Contrasts were extracted from seasonal effect. 
```{r S6,echo= FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
source('functions.R')
# bring in, combined and rename tables
data.gam <- readRDS(file = "Final.Analysis/Final.Figure.data/data.temp.gam.analysis.rds")
# top model
Season.Sex.Interaction.Povi <- readRDS(file = "Models/Season.Sex.Interaction.Povi.rds")
# gam info
data.gam$fit <- predict(Season.Sex.Interaction.Povi, type = "response")
data.gam$se <- predict(Season.Sex.Interaction.Povi, type = "se")
# summarizing To by id, Sex, Season
Pmax <- data.gam %>% 
  group_by(POVI, Sex, Season) %>% 
  filter(fit == max(fit)) %>% 
  rename(Pmax = fit)
Pmax.final <- Pmax %>% 
  group_by(POVI, Sex, Season) %>% 
  summarise(Pmax.temp = mean(Tb),
            Pmax = mean(Pmax))
#######
# analysis for Pmax - speed
pmax.mod <- lmer(Pmax  ~ Season + Sex + Season*Sex  + (1|POVI), Pmax.final)
pmax.anova <- extract_anova_dataframe(model =  pmax.mod)

# significant seasona and interaction
Pmax.Sex.Season <- emmeans(pmax.mod, pairwise ~ Sex |Season) 
# extracting season sex contrasts
Pmax.Sex.Season.df <- as.data.frame(Pmax.Sex.Season$emmeans) %>% 
  select(c(Season, emmean, SE, Sex, lower.CL, upper.CL))
# extracting seasonal contrasts
Pmax.Season <- emmeans(pmax.mod, pairwise ~ Season)
Pmax.Season.df <- as.data.frame(Pmax.Season$contrasts)
Pmax.Season.df <- Pmax.Season.df %>% mutate_if(is.numeric, ~round(., 2))
Pmax.Season.df[2:6,6]= "<0.01"

# final table using Pmax analysis
TableS6 <- Pmax.Season.df %>% rename("Contrast" = contrast, "Estimate" = estimate, "t Ratio" = t.ratio, "p value" = p.value)

# Table S6 Final table
Tbl.S6 <-flextable(TableS6) %>% 
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues()
knitr::knit_print(Tbl.S6)
```
\newpage
Table S7. Tukey-Kramer multiple comparisons from Topt model that accounted for season, sex and the interaction.  
```{r S7,echo= FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
# bring in, combined and rename tables
data.gam <- readRDS(file = "Final.Analysis/Final.Figure.data/data.temp.gam.analysis.rds")
# top model
Season.Sex.Interaction.Povi <- readRDS(file = "Models/Season.Sex.Interaction.Povi.rds")
data.gam$fit <- predict(Season.Sex.Interaction.Povi, type = "response")
data.gam$se <- predict(Season.Sex.Interaction.Povi, type = "se")
# summarizing To by id, Sex, Season
Pmax <- data.gam %>% 
  group_by(POVI, Sex, Season) %>% 
  filter(fit == max(fit)) %>% 
  rename(Pmax = fit)
Pmax.final <- Pmax %>% 
  group_by(POVI, Sex, Season) %>% 
  summarise(Pmax.temp = mean(Tb),
            Pmax = mean(Pmax))
#######
# analysis for Topt - speed
To.mod <- lmer(Pmax.temp  ~ Season + Sex + Season*Sex  + (1|POVI), Pmax.final)
To.mod.sum <- as.data.frame(anova(To.mod)) # no differences between sex, but significant seasona and interaction
Pmax.Sex.Season <- emmeans(To.mod, pairwise ~ Sex |Season) 
# extracting season sex contrasts
Pmax.Sex.Season.df <- as.data.frame(Pmax.Sex.Season$emmeans) %>% 
  select(c(Season, emmean, SE, Sex, lower.CL, upper.CL))
# extracting seasonal contrasts
Pmax.Season.sex <- emmeans(To.mod, pairwise ~ Sex| Season)
Pmax.Season.sex.df <- as.data.frame(Pmax.Season.sex$contrasts)
Pmax.Season.sex.df <- Pmax.Season.sex.df %>% mutate_if(is.numeric, ~round(., 2))

# final table using Pmax analysis
TableS7 <- Pmax.Season.sex.df %>% rename("Contrast" = contrast, "Estimate" = estimate, "t Ratio" = t.ratio, "p value" = p.value)

# TableS7 Final table
Tbl.S7 <-flextable(TableS7) %>% 
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S7)
```
\newpage
Table S8. Model comparisons of spring survival probability (φ) for *Pogona vitticeps*, depending on sex, movement (mins), accuracy of thermoregulation (de), effectiveness of thermoregulation (E), and maximum performance (Pmax). Sex interactions for d_b and E were accounted for because of the differences between males and females during the spring (Table 1). Values within the brackets are nested variables and variables outside of brackets are covariates. Bold values indicate values were considered to have support (ΔAICc of < 2.0).
```{r Table3,echo= FALSE}
# bring in, combined and rename tables
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
#Mark Table
TableS8 <- read.csv(file ="Final.Analysis/Final.Figure.data/MARK.Table.csv", dec = "2") %>%
  rename("Delta AICc" = Delta.AICc, "AICc Weights" = AICc.Weights, "Model Likelihood" = Model.Likelihood, "Number of Parameters" = Num..Par)

# TableS8 Final table
Tbl.S8 <-flextable(TableS8) %>% 
  autofit(part = "all") %>% 
  fit_to_width(7.0)%>%
  align(align ="center", j = c(2,3,4,5,6)) %>% 
  bold(bold = TRUE, i = c(1:3)) %>%
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S8)
```

\newpage
```{r S1fig, echo = FALSE, include = FALSE}
setwd("~/Dropbox/RWorkingDirectory/TPC_Survival/R")
#save this figure in the correct folder and bring in to knit
knitr::include_graphics("Final.Analysis/Final.Figures/FigS1_Te_Tepredict.pdf")
```
Figure S1. 

\newpage
```{r S2fig,echo= FALSE}
#############
setwd("~/Dropbox/PhD Pogona/Dissertation/4.Thermal_chapter/R")
# bring in and arrange data
db.sex.all.final <- readRDS(file = "Final.Analysis/Final.Figure.data/db.final.RDS")
Te <-read.csv(file = "Te_models/Te.All.Final.csv") %>% 
  rename(Te=Value)
Te$Season <- plyr::revalue(Te$Month, c("June" = "Winter",
                                       "July" = "Winter",
                                       "August" = "Winter",
                                       "September" = "Spring", 
                                       "October" = "Spring", 
                                       "November"= "Spring",
                                       "December" = "Summer", 
                                       "January" =  "Summer",
                                       "February" = "Summer",
                                       "March" = "Autumn", 
                                       "April" = "Autumn", 
                                       "May" = "Autumn"))
#format date and filter to fit accelerometer date "2019-09-01" and times between 0500 - 2100
Te$Date <- dmy(Te$Date)
Te <- Te %>% 
  filter(Date < "2019/09/01") %>% 
  filter(Time >= 5) %>% 
  filter(Time <= 21) %>% 
  mutate(HR = Time)
min(Te$HR)
max(Te$HR)
  
# pre calibration fig
Fig <- Te %>%
  group_by(Date, Season)%>%
  summarise(Max = max(Te),
            Min = min(Te),
            Mean = mean(Te)) 
Fig.tb <- db.sex.all.final %>% 
  group_by(Date, Season) %>% 
  summarise(Max = max(Tb),
            Min = min(Tb),
            Mean = mean(Tb)) %>%
  ungroup()
Fig.tb <- Fig.tb %>% 
  filter(Date>"2018-10-09")


###############
# COOL HOT TB AND TE FIG
# Te ribbon and d
Fig.S7 <- ggplot(Fig, aes( x = Date, y = Mean)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = Min, ymax = Max), alpha = 0.2)  +
  geom_line(data = Fig.tb, aes(x = Date, y = Mean), linetype = "longdash", color = "green")+
  geom_line(data = Fig.tb, aes(x = Date, y = Min), linetype = "dotted", color = "blue")+
  geom_line(data = Fig.tb, aes(x = Date, y = Max), linetype = "dotted", color = "red")+
  scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y")+
  scale_y_continuous(breaks=c(-10, 0, 10, 20, 30, 40, 50, 60, 70))+
  coord_cartesian(ylim = c(-10, 70))+
  labs(x = NULL, y = "Temperature (°C)")+
  theme(aspect.ratio = 1)+
  theme_bw()

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("./Final.Analysis/Final.Figures/")
```
Figure S2. Environmental temperature range and how adult *Pogona vitticeps* thermoregulated during the duration of the study. Black solid lines represent the grand mean environmental temperatures of operative models (Te) for each day and grey bands represent the daily mean minimum and maximum of Te. Coloured lines represent the daily grand mean (green), mean minimum (blue), and mean maximum (red) predicted body temperatures Tb Predict for all lizards during the study.